### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

\subsubsection{Identifying Affected Balls}
\label{subsubsec-affball}

We first develop procedure \identifyaffball to identify \affballsx,
which utilizes auxiliary structures \fb and \bfc.

@@

\vspace{-.5ex}

\subsubsection{Updating Fragment-Ball Matches}
\label{subsubsec-updtm}

We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
by procedure \incmatch.

@@

\subsubsection{Combining Fragment-Ball Matches}
\label{subsubsec-combine}

Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb. Observe that only the balls from \affballsx that match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.

@@

\subsubsection{Early Return Optimization Technique}
\label{subsubsec-Inc-opt}

%As introduced in last section, the {\em lazy update manner} accelerates the process to return updated top-$k$ perfect subgraphs by postponing the processing of each unit pattern update.
We propose an optimization technique for \incp to further speed-up the incremental computations, by making use of the top-$k$ semantics.
%
We first define {\em early return} for incremental top-$k$ algorithms, analogous to {\em early termination} for batch top-$k$ algorithms~\cite{FaginLotem03}.

@@

\subsubsection{The Complete Algorithm for Pattern Updates}
\label{subsubsec-completedynamicP}

Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,
algorithm \incp computes the maximum match relations of $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.

>>>>

%\subsubsection{Identifying Affected Balls}
%\label{subsubsec-affball}

\stab{\bf (1) Identifying affected balls}. 
We first develop procedure \identifyaffball,
which utilizes auxiliary structures \fb and \bfc, to identify \affballsx.

@@

%\vspace{-2ex}
%\subsubsection{Updating Fragment-Ball Matches}
%\label{subsubsec-updtm}

\stab{\bf (2) Updating Fragment-Ball matches}. We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
by procedure \incmatch.

@@

%\subsubsection{Combining Fragment-Ball Matches}
%\label{subsubsec-combine}

\stab{\bf (3) Combining Fragment-Ball matches}. Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb. Observe that only the balls from \affballsx that match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.

@@

%\subsubsection{Early Return Optimization Technique}
%\label{subsubsec-Inc-opt}

\stab{\bf (4) Early return optimization technique}. 
%As introduced in last section, the {\em lazy update manner} accelerates the process to return updated top-$k$ perfect subgraphs by postponing the processing of each unit pattern update.
We propose an optimization technique for \incp to further speed-up the incremental computations, by making use of the top-$k$ semantics.
%
We first define {\em early return} for incremental top-$k$ algorithms, analogous to {\em early termination} for batch top-$k$ algorithms~\cite{FaginLotem03}.

@@

%\subsubsection{The Complete Algorithm for Pattern Updates}
%\label{subsubsec-completedynamicP}

\stab{\bf (5) The complete algorithm for pattern updates}.
Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,
algorithm \incp computes the maximum match relations of $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.
